Untitled

### 2023-12-31 code/analysis_Redo.Rmd
updating heterogeneity access analysis

   model.dist.quants <-  did2s(
      data = df.spill3 %>% filter(Dist == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)), 
      yname = "Medicaid", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    )
    tes <- data.frame(model.dist.quants$coeftable)[1,]

  for (i in 1:4){
      model.dist.quants <-  did2s(
      data = df.spill3  %>% filter(Dist > quantile(Dist, qnats1[i]) & Dist <= quantile(Dist, qnats2[i]))%>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1))  , 
      yname = "Medicaid", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    ) 
      tes <- rbind(tes, data.frame(model.dist.quants$coeftable)[1,])
  }

@@

zp1 <- event_study(data = df.spill3 %>% filter(Dist > quantile(Dist, 0.8)), 
  yname = "Sites", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
  filter(abs(term) < 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Locations in Farthest 20% of Zips")+ xlab("Year Relative to Competitive Shock") + ylab("Number of Locations")

zp2 <- event_study(data = df.spill3 %>% filter(Dist == 0), 
  yname = "Sites", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
  filter(abs(term) < 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Locations in Competitive Zip")+ xlab("Year Relative to Competitive Shock") + ylab("Number of Locations")

zp3 <- event_study(data = df.spill3 %>% filter(Dist > quantile(Dist, 0.8)) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites)), 
  yname = "Total.Hours", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
  filter(abs(term) < 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Hours per Week in Farthest 20% of Zips")+ xlab("Year Relative to Competitive Shock") + ylab("Hours per Week")

@@

zp <- ggarrange(zp1, zp2, zp3, zp4, common.legend = TRUE)
zp <- ggarrange(zp3, zp4, common.legend = TRUE)

>>>>

   model.dist.quants <-  did2s(
      data = df.spill3 %>% filter(Dist == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)), 
      yname = "NumberofPatients", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    )
    tes <- data.frame(model.dist.quants$coeftable)[1,]

  for (i in 1:4){
      model.dist.quants <-  did2s(
      data = df.spill3  %>% filter(Dist > quantile(Dist, qnats1[i]) & Dist <= quantile(Dist, qnats2[i]))%>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1))  , 
      yname = "NumberofPatients", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    ) 
      tes <- rbind(tes, data.frame(model.dist.quants$coeftable)[1,])
  }

@@

zp1 <- event_study(data = df.spill3 %>% filter(Dist > quantile(Dist, 0.9)), 
  yname = "NumberofPatients", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
  filter(abs(term) < 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Locations in Farthest 20% of Zips")+ xlab("Year Relative to Competitive Shock") + ylab("Number of Locations")

zp2 <- event_study(data = df.spill3 %>% filter(Dist == 0), 
  yname = "NumberofPatients", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
  filter(abs(term) < 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Locations in Competitive Zip")+ xlab("Year Relative to Competitive Shock") + ylab("Number of Locations")

zp3 <- event_study(data = df.spill3 %>% filter(Dist > quantile(Dist, 0.9)) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites)), 
  yname = "Total.Hours", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
  filter(abs(term) < 7) %>% 
  filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Hours per Week in Farthest 10% of Zips")+ xlab("Year Relative to Competitive Shock") + ylab("Hours per Week")

@@

zp <- ggarrange(zp1, zp2, zp3, zp4, common.legend = TRUE)

zp <- ggarrange(zp3, zp4, common.legend = TRUE)
